getdata3.Rmd

### 2021-12-30 getdata3.Rmd
reduce variable list

```{r fromobs}
bobs <- obs[obs$starttyp == 2 & obs$id %in% per$id, ]
indx <- match(per$id, bobs$id)
per$socStatus <- bobs$socStatus[indx]
per$hisclass <- bobs$hisclass[indx]
per$nofrs <- bobs$nofrs[indx]
per <- per[!is.na(per$nofrs), ]
per$subreg <- factor(per$nofrs)
levels(per$subreg) <- c(rep("ume", 2), 
                        rep("bjur", 4), 
                        rep("sten", 3))
per <- per[(per$subreg != "sten"), ]
per$subreg <- factor(per$subreg)
per$enter <- 0
per$sex <- factor(per$kon, labels = c("boy", "girl"))
per$birthdate <- toTime(per$birthdate)
per$illeg <- as.numeric(per$ab == 2)
per$parity <- per$paritet_g
saveRDS(per, file = "data/infdat3.rds")
```

@@

bume$region <- "ume"
bskel$region <- "ske"
infdat <- rbind(bume, bskel)
infdat <- infdat[order(infdat$id, infdat$enter), c("region", "id", "sex", "enter", "exit", "event", 
                                                   "birthdate", "socStatus", "hisclass", "illeg",
                                                   "parity", tempvars)]
saveRDS(infdat, file = "data/infdat3_year3.rds")

>>>>

```{r fromobs}
bobs <- obs[obs$starttyp == 2 & obs$id %in% per$id, ]
indx <- match(per$id, bobs$id)
per$socStatus <- bobs$socStatus[indx]
per$hisclass <- bobs$hisclass[indx]
per$nofrs <- bobs$nofrs[indx]
per <- per[!is.na(per$nofrs), ]
per$subreg <- factor(per$nofrs)
levels(per$subreg) <- c(rep("ume", 2), 
                        rep("bjur", 4), 
                        rep("sten", 3))
per <- per[(per$subreg != "sten"), ]
per$subreg <- factor(per$subreg)
per$enter <- 0
per$sex <- factor(per$kon, labels = c("boy", "girl"))
per$birthdate <- toTime(per$birthdate)
per$illeg <- as.numeric(per$ab == 2)
per$parity <- per$paritet_g
per$paritet_g <- per$paritet_k <- per$doddat <- per$frsbosdat <- NULL
per$fid <- per$fboort <- per$ab <- per$fyrkfd <- per$fyrkind <- NULL
per$region <- per$kon <- per$fodhfrs <- per$frsbobdat <- per$frsbostyp <- NULL
per$fbonmn <- per$fboind <- per$fyrkrel <- per$fyrketxt <- NULL
per$foddat <- as.Date(as.character(per$foddat), format = "%Y%m%d")
per <- per[, c("id", "sex", "birthdate", "mid", "foddat", "parity", "illeg", 
               "subreg", "socStatus", "enter", "exit", "event")]
saveRDS(per, file = "data/infdat3.rds")
```

@@

bume$region <- "ume"
bskel$region <- "ske"
infdat <- rbind(bume, bskel)
infdat <- infdat[order(infdat$id, infdat$enter), c("subreg", "id", "sex", "enter", "exit", "event", 
                                                   "birthdate", "socStatus", "illeg",
                                                   "parity", tempvars)]
saveRDS(infdat, file = "data/infdat3_year3.rds")
